### 2016-09-01 doc/publications/plos16/plos16.tex
spelling

RF are very easy to parallize. As the forest is a sum of descision trees, it it possible to grow separate trees on 
each processor and sum them. This mode of parallization is widely used for the {\sc random forest} implementation in
R~\cite{}, and could also be used for the {\sc party}~\cite{} package.
\marginpar{Rob, Piotr can you extend this with some more detailed descriptions of party and RF in R}
 However,
this has several limitations. One is that these implementations reach a hard limit in R when they require vectors of a
length greater than $2^{31}-1$. While R now has basic support for long vectors, not all fuctions can utilize it.
These traditional implementations are have been reported to not scale well with increasing feature
size~\cite{Wright.and.Ziegle.2016}.

However a more basic problem may be that the parallization is at too course a grain. The Cursed Forest implemtation has
a finer grained version of paraliization where the calculation for each split is handed off ot a separate processor.

>>>>

RF are very easy to parallize. As the forest is a sum of decision trees, it it possible to grow separate trees on 
each processor and sum them. This mode of parallization is widely used for the {\sc random forest} implementation in
R~\cite{}, and could also be used for the {\sc party}~\cite{} package.
\marginpar{Rob, Piotr can you extend this with some more detailed descriptions of party and RF in R}
 However,
this has several limitations. One is that these implementations reach a hard limit in R when they require vectors of a
length greater than $2^{31}-1$. While R now has basic support for long vectors, not all functions can utilize it.
These traditional implementations are have been reported to not scale well with increasing feature
size~\cite{Wright.and.Ziegle.2016}.

However a more basic problem may be that the parallization is at too course a grain. The Cursed Forest implementation has
a finer grained version of parallization where the calculation for each split is handed off to a separate processor.
